Networked Character Devices

### 2011-12-10 report/paper.tex
paper: abstract

\begin{abstract}
Lorem ipsum
\end{abstract}

@@

>>>>

\begin{abstract}
While there are various projects which provide a network abstraction layer for
specific high-level subsystems in the Linux kernel, there aren't any low-level
general purpose solutions. Network character devices (NCD) is a system for
exporting character device drivers of a fast, local network. However NCD works
to some extent with regular files, block devices, sockets, and pipes; it is also
suitably responsive over Internet connections for many applications.
\end{abstract}

@@

% vim: set ts=2 sts=2 sw=2 et spell tw=72 : %
